### 2017-02-08 manuscript.rmd
added funding

Thanks to Steve Haddock, Alex Damian Serrano, August Guang, Bruno Vellutini, and Zack Lewis for feedback on the manuscript. This work was supported by the National Science Foundation (DEB-1256695 and the Waterman Award).

>>>>

Thanks to Steve Haddock, Alex Damian Serrano, August Guang, Bruno Vellutini, and Zack Lewis for feedback on the manuscript. CWD's contribution was supported by the National Science Foundation (DEB-1256695 and the Waterman Award). AH was supported by the European Research Council Community’s Framework Program Horizon 2020 (2014–2020) ERC grant agreement 648861.
\pagebreak
